DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2017-02-13 2015CompleteDerivation/completeDerivation.tex
Removing mention of Galilean/Lorenz transformations

The third case is when we perform a state variable transformation $\hat{q}=\hat{q}(q,t)$ that is time dependent (e.g. $\hat{q}=q+vt$). Our composite state distribution $\rho(q)$ becomes $\rho(\hat{q},t)$: it is no longer defined at equal time. This means that our measure $\mu$ needs to be modified to define integrals over the time variable.\footnote{Looking ahead, another way to frame the problem is that Galilean transformations do not preserve phase space volume. Lorentz transformations, on the other hand, do \cite{Treumann}.}

@@

\bibitem{Treumann} Treumann, R. A., Nakamura, R., Baumjohann,  W.: Relativistic transformation of phase-space distributions. Annales Geophysicae (2011)

>>>>

The third case is when we perform a state variable transformation $\hat{q}=\hat{q}(q,t)$ that is time dependent (e.g. $\hat{q}=q+vt$). Our composite state distribution $\rho(q)$ becomes $\rho(\hat{q},t)$: it is no longer defined at equal time. This means that our measure $\mu$ needs to be modified to define integrals over the time variable.

@@

%\bibitem{Treumann} Treumann, R. A., Nakamura, R., Baumjohann,  W.: Relativistic transformation of phase-space distributions. Annales Geophysicae (2011)
